Music Perception: Stimuli profiles

### 2021-03-04 material/expstimuli/stimuli.Rmd
round time2
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

# stimuli for practice trials
for (i in 73:80){ # 4 stimuli for each category
  subject = list_include$SubNr[i]
  block = list_include$BlockNr[i]
  trial = list_include$TrialNr[i]
  cond = list_include$Condition[i]
  skill = list_include$Skill[i]
  current <- dt_include[SubNr == subject & BlockNr == block & TrialNr == trial]
  firstTimestamp = current$TimeStamp[1]
  current$TimeStamp <- current$TimeStamp - firstTimestamp # start with time 0

@@

data <- all_data[event == "Note On" | event == "Note Off"]
data$NoteNr <- rep(1:144, nrow(data)/144)
data$channel <- NULL
data$parameterMetaSystem <- NULL
data$track <- NULL
data$type <- NULL
data$time2 <- (data$time/960)*1000 # deltatime to time (ms)

>>>>

# stimuli for practice trials
for (i in 73:80){ # 2 stimuli for each category
  subject = list_include$SubNr[i]
  block = list_include$BlockNr[i]
  trial = list_include$TrialNr[i]
  cond = list_include$Condition[i]
  skill = list_include$Skill[i]
  current <- dt_include[SubNr == subject & BlockNr == block & TrialNr == trial]
  firstTimestamp = current$TimeStamp[1]
  current$TimeStamp <- current$TimeStamp - firstTimestamp # start with time 0

@@

data <- all_data[event == "Note On" | event == "Note Off"]
data$NoteNr <- rep(1:144, nrow(data)/144)
data$channel <- NULL
data$parameterMetaSystem <- NULL
data$track <- NULL
data$type <- NULL
data$time2 <- round((data$time/960)*1000) # deltatime to time (ms)
